### 2017-10-15 mcmc.tex
typo; less math

For example, one magical property of a sampling (in a $D$-dimensional
space) is that a \emph{histogram} (a $D$-dimensional histogram) of the
samples (divided, if you like, by the number of samples in each bin
and the bin width\note{We are referring here to the point that if you
  want a histogram of samples to look just like the posterior pdf from
  which the samples are drawn, the histogram (thought of as a step
  function) must integrate to unity.}  looks very much like the pdf
from which the samples were drawn.
This is a way to ``reconstruct'' the pdf from the sampling:
Make a histogram from the samples.
Even in this case, the sampling is being used to do \emph{integrals};
  the (possibly odd) idea is that the approximate or effective value of the pdf in each bin
  of the histogram is an average over the bin.
That average is obtained by performing an integral.

>>>>

For example, one magical property of a sampling (in a $D$-dimensional
space) is that a \emph{histogram} (a $D$-dimensional histogram) of the
samples (divided, if you like, by the number of samples in each bin
and the bin width\note{We are referring here to the point that if you
  want a histogram of samples to look just like the posterior pdf from
  which the samples are drawn, the histogram (thought of as a step
  function) must integrate to unity.})
looks very much like the pdf from which the samples were drawn.
This is a way to ``reconstruct'' the pdf from the sampling:
Make a histogram from the samples.
Even in this case, the sampling is being used to do \emph{integrals};
  the (possibly odd) idea is that the approximate or effective value of the pdf in each bin
  of the histogram is an average over the bin.
That average is obtained by performing an integral.
